### 2016-07-28 main.tex

\item[Runtime:]\hfill
  \begin{description}
  \item[MATLAB:] {\tt https://github.com/gardner-lab/syllable-detector-matlab}
    \marginpar{Jeff: Can you flesh this out?}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
    \item[Usage:]\hfill
    \end{description}
  \item[Swift:] {\tt https://github.com/gardner-lab/syllable-detector-swift}
    \marginpar{Nathan: Can you flesh this out?}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item Connect the microphone through a preamp to {\em FIXME the left channel of the stereo audio input jack on the Mac Mini?}.
      \item {\em FIXME} How to connect the Arduino?  Add the Arduino programme to your GitHub?
      \item {\em FIXME} How to connect if not using Arduino?
      \end{itemize}
    \item[Usage:]\hfill
      \begin{itemize}
      \item Use {\tt convert\_to\_text.m} to convert the Matlab output file to a format easily readable by Swift.
      \item {\em FIXME} How to start Swift?  Parameters?
      \end{itemize}
    \end{description}
  \item[LabVIEW:] {\tt https://github.com/bwpearre/birds/align}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item The microphone should be connected through a preamplifier to the data acquisition card, by default on Analog Input 0 (AI0).
      \item Outputs are on the Digital I/O (DIO) channels.  See the block diagram of {\tt nnfft.vi} for documentation, or just connect to DIO0.
      \end{itemize}
    \item[Usage:]\hfill
      Use LabVIEW to open {\tt nnfft.vi}.  A file
      chooser is provided in the front panel.  Use it to point to the network file
      produced by {\tt learn\_detector.m}, and use LabView's ``Run''
      button to begin detection.
    \end{description}
  \end{description}

>>>>

\item[Runtime:]\hfill
  \begin{description}
  \item[MATLAB:] {\tt https://github.com/gardner-lab/syllable-detector-matlab}
    \marginpar{Jeff: Can you flesh this out?}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
    \item[Usage:]\hfill
    \end{description}
  \item[Swift:] {\tt https://github.com/gardner-lab/syllable-detector-swift}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Download the most recent release from the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item Either connect the microphone directly into the microphone jack or through a 
      preamp into the audio input jack. If the input jack supports multiple channels (e.g., 
      audio input jacks are usually stereo), you can connect multiple audio sources and run 
      different detectors on each channel simultaneously.
      \item To generate TTL signals via the audio output, use the headphone jack. The 
      audio output must have at least the same number of channels as the input.
      \item To generate TTL signals via an Arduino, load the MATLAB arduino IO sketch 
      onto the Arduino (the sketch is available in the Github repository, and provides a 
      simple serial protocol for controlling pins). Connect the Arduino 
      to the computer via USB. The TTL signal for the first input will be available on 
      pin 7, the second input on pin 8, etc.
      \end{itemize}
    \item[Usage:]\hfill
      \begin{itemize}
      \item Use {\tt convert\_to\_text.m} to convert the Matlab output file to a format 
      easily readable by Swift. This will generate a text version of the neural network.
      \item Launch the application downloaded above. It will provide an 
      menu to select an audio input and either an audio output or an Arduino output (if 
      detected). Once you select an input and an output, a new window will show all audio 
      channels associated with the input. For each channel, select a the text-encoded version of 
      the detector created in the previous step. Once configured, press run to begin 
      monitoring the inputs.
      \end{itemize}
    \item[Customization:]\hfill
      \begin{itemize}
      \item You can clone the Github repository and use Xcode to edit the project, if you 
      are interested in extending or modifying the functionality. To hook into either 
      the raw input or output, look at the ``ViewControllerProcessor.swift'' file. The 
      {\tt Processor} class acts as a coordinator, receiving income audio, passing that
      to the detector and generating appropriate output TTL signals.
      \end{itemize}
    \end{description}
  \item[LabVIEW:] {\tt https://github.com/bwpearre/birds/align}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item The microphone should be connected through a preamplifier to the data acquisition card, by default on Analog Input 0 (AI0).
      \item Outputs are on the Digital I/O (DIO) channels.  See the block diagram of {\tt nnfft.vi} for documentation, or just connect to DIO0.
      \end{itemize}
    \item[Usage:]\hfill
      Use LabVIEW to open {\tt nnfft.vi}.  A file
      chooser is provided in the front panel.  Use it to point to the network file
      produced by {\tt learn\_detector.m}, and use LabView's ``Run''
      button to begin detection.
    \end{description}
  \end{description}
